Programming Language Foundations in Agda

### 2019-07-14 papers/scp/PLFA.tex
Halfway through adding material on experience teaching the course

>>>>

\section{Experience}

Philip now has five years of experience teaching from SF and one year
teaching from PLFA.  He taught three courses from PLFA.
\begin{itemize}
\item
  University of Edinburgh, September--December 2018 (with teaching
  assistance from Wen and Chad Nester); twenty two-hour slots, one
  hour of lecture followed by one hour of lab. Ten students completed
  the course, which covered Parts~I and~II of PLFA.

\item
  Pontifícia Universidade Católica do Rio de Janeiro (PUC-Rio),
  March--July 2019, hosted by Roberto Ieuramalischy; ten three-hour
  slots, two hours of lecture followed by one hour of lab.  Ten
  students completed the course, which covered Parts~I and~II of PLFA,
  save students read chapter Lists on their own, and chapter
  Bisimilarity was skipped.

\item University of Padova, June 2018, hosted by Maria Emilia Maietti;
  two three-hour slots, two hours of lecture followed by one hour of
  lab.  About thirty students sat the course. Covered chapters
  Naturals, Induction, and Relations.

\end{itemize}
In addition, David Darais at University of Vermont and John Leo at
Google Seattle have taught from PLFA.

Exercises in PLFA are classified in three ways.
\begin{itemize}
\item
  Exercises labelled “(recommended)” are the ones students are
  required to do in the classes taught at Edinburgh and PUC-Rio.

\item
  Exercises labelled “(stretch)” are there to provide an extra
  challenge. Few students do all of these, but most attempt at least a
  few.  Ten students completed the course.

\item   
  Exercises without a label are included for those who want extra
  practice.  To Philip's surprise, students at PUC-Rio completed
  quite a few of these.
\end{itemize}
Students are expected to complete coursework for all of the
required questions in the text, optionally doing any stretch or
unlabelled exercises. Coursework also includes a ``mock mock''
exam, as described below.

The mark for the course is based on coursework and a final-exam,
weighted 1/4 for coursework and 3/4 for the final exam.  The weighting
for coursework is designed to be high enough to encourage students to
do it (they all do), but not so high as to encourage cheating.
Students are encouraged to help each other with coursework.

The final-exam is two hours online. Students have access to the Agda
proof assistant to check their work.  At Edinburgh, students use
computers with a special exam operating system that disables access
to the internet.  Students are given access to the text of PLFA,
the Agda standard libraries, and the Agda language reference manual,
but no other materials.

Students must answer question 1 on the exam, and one of questions 2 or
3.  Question 1 gives predicates over a data structure, such lists or
trees, to be formalised in Agda, and a theorem relating the
predicates, to be formalised and proved in Agda.  Question 2 gives the
students the intrinsic formulation of lambda calculus from chapter
DeBruijn, which they must extend with a described language feature.
Question 3 give the students the the bidirectional type inferencer
from chapter Inference, which they must extend with a described
language feature.

Because the course is taught using a proof assistant, it is important
that the students have access to a proof assistant during the
exam. The whole point of a proof assistant is to avoid
errors. Students are told in advance that they are expected to get
perfect on the exam, and that they will have to study hard to achieve
this level.  Given that the goal of formal methods is to avoid error,
we think a pedagogical purpose is served by telling the students that
they are expected to achieve perfection and making it possible for
them to do so.

they are expected to answer
one question about formalising predicates on a data structure such
as lists or tree

The coursework is assigned 1/4 of the
total mark of the course: enough to encourage the students to do
it, but not enough to make it worth cheating. The remaining 3/4 of
the tot

Most of the marks are base

There is also a ``mock mock'' exam
assigned as cou

The coursework was broken into four or five clusters, one due every
few weeks. There is also a coursework consisting of a ``mock mock''
exam, see below.

recommended
At Edinburgh and PUC-Rio, students completed coursework based on
